---
title: "Enzymatic conversion kinetics in Mushroom Waste Upcycling"
author: "Sarah"
date: "2025-10-01"
format: html
---

This is a quarto report talking about some of my research with mushroom waste upcycling.


# PROJECT DESCRIPTION
This project explores an up-cycling process of the solid mushroom waste called spent mushroom substrate (SMS).
By using enzymes such as cellulase and hemicellulases we can break down the plant material inside the SMS.
This gives us a yield of sugars like glucose and xylose and allows us to ferment sugars into biopolymers or biofuel through other microorganisms.

## Method design

The data for this project was obtained by taking a sample of the hydrolysate (the liquidy, sugary stuff) at regular intervals within the 72hour incubation period.
The samples were then analysed for the amount of glucose and xylose, giving us an enzymatic conversion kinetic.

In this study we used and compared three different categories of SMS from two different mushroom species.
Shiitake SMS was untreaded, while oystermushroom SMS was treated with a post-hydrolysis using two different conditions.


```{r}
#| echo: false

figure1 <- readRDS("./figures/suger_kinetic_1.RDS")

figure1
```


```{r}
#| echo: false

figure2 <- readRDS("./figures/suger_kinetic_2.RDS")

figure2
```


```{r}
#| echo: false

figure2 <- readRDS("./figures/suger_kinetic_2.RDS")

figure2
```
